The Prevalence of E-Mail Header Injections on the World Wide Web

### 2016-05-19 Discussion/lessons.tex
final data update

\subsection{Lessons Learned}
    From our results, it is evident that the vulnerability exists in the wild. Despite its relatively low occurrence rate compared to the more popular SQL Injection and XSS (Cross-Site Scripting), when we take the total number of websites on the World Wide Web --- 1,018,863,952 according to Internet Live Stats~\cite{InternetLiveStats2016} as of early 2016 --- and calculate \successDelta\ percent (the occurrence rate of E-Mail Header Injection vulnerability as found by our system) of that number, we end up with 11,309,390 websites - a pretty significant number. We agree that an extrapolation of that kind might not be an accurate measure of the prevalence of the vulnerability. However, even with as few as a thousand websites affected by this vulnerability, it can still have a disastrous impact on these websites, and also on overall World Wide Web due to the traffic caused by the sheer number of generated e-mails.

@@

    The second attack is an interesting one, as this has not yet been documented, and provides the ability to inject multiple e-mail addresses into only the \texttt{To} field. We christened this as \texttt{To header injection}. In this form of the vulnerability, we are able to simply add addresses to the \texttt{To} field of the form with newlines separating the e-mail addresses. Whether this particular form of the vulnerability is found due to the websites in question, or whether this is an implementation issue with a particular language or framework, is unclear. However, from our preliminary analysis, it is evident that these websites do not share much with respect to the languages and frameworks used. 
    Even in this form of the attack, we are still able to extract information that should be private to a given user, and in some of these cases, able to inject enough data to spoof the first few lines of the e-mail message. From Table~\ref{tab:analysis}, information leakage using \texttt{To header injection} was possible on 142 forms, while spoofing using \texttt{To header injection} was possible on 11 forms.

>>>>

\subsection{Lessons Learned}
    From our results, it is evident that the vulnerability exists in the wild. Despite its relatively low occurrence rate compared to the more popular SQL Injection and XSS (Cross-Site Scripting), when we take the total number of websites on the World Wide Web --- 1,018,863,952 according to Internet Live Stats~\cite{InternetLiveStats2016} as of early 2016 --- and calculate \successDelta\ percent (the occurrence rate of E-Mail Header Injection vulnerability as found by our system) of that number, we end up with 14,875,413 websites - a pretty significant number. We agree that an extrapolation of that kind might not be an accurate measure of the prevalence of the vulnerability. However, even with as few as a thousand websites affected by this vulnerability, it can still have a disastrous impact on these websites, and also on overall World Wide Web due to the traffic caused by the sheer number of generated e-mails.

@@

    The second attack is an interesting one, as this has not yet been documented, and provides the ability to inject multiple e-mail addresses into only the \texttt{To} field. We christened this as \texttt{To header injection}. In this form of the vulnerability, we are able to simply add addresses to the \texttt{To} field of the form with newlines separating the e-mail addresses. Whether this particular form of the vulnerability is found due to the websites in question, or whether this is an implementation issue with a particular language or framework, is unclear. However, from our preliminary analysis, it is evident that these websites do not share much with respect to the languages and frameworks used. 
    Even in this form of the attack, we are still able to extract information that should be private to a given user, and in some of these cases, able to inject enough data to spoof the first few lines of the e-mail message. From Table~\ref{tab:analysis}, information leakage using \texttt{To header injection} was possible on 163 forms, while spoofing using \texttt{To header injection} was possible on 13 forms.

### 2016-05-19 Results/analysis.tex
final data update

	\item E-Mails with the \texttt{to} header successfully injected\\
	We discovered an unintended vulnerability which we would like to christen \texttt{TO~header injection}. These injections reflect the ability to inject any number of e-mail addresses into the \texttt{to} field while being unable to inject any other header into the e-mails. We attribute this behavior to inconsistent sanitization by the application. 
	The vulnerability is further aided by the leniency shown by mail servers, wherein they parsed malformed e-mail addresses and delivered it to the right mail server, and on the receiving end, the mail was delivered to the right mailbox.

	While not allowing us complete control over the e-mails sent, \texttt{TO header injection} makes it possible to append any number of e-mail addresses, thereby enabling us to leak information, and/or perform DoS (Denial of Service) attacks.

@@

\input{Results/data_analysis}
We explain the combination of these header injections (4-7) as follows:
\begin{itemize}
	\item E-Mail Header Injections with \texttt{bcc} and \texttt{x-check} headers\\
	These represent the perfect attack scenario where we are able to inject multiple headers into the e-mails. We can see that over 75\% of the received \texttt{bcc} header injected e-mails are also susceptible to other header injections.

>>>>

	\item E-Mails with the \texttt{to} header successfully injected\\
	We discovered an unintended vulnerability which we would like to christen \texttt{To~header injection}. These injections reflect the ability to inject any number of e-mail addresses into the \texttt{to} field while being unable to inject any other header into the e-mails. We attribute this behavior to inconsistent sanitization by the application. 
	The vulnerability is further aided by the leniency shown by mail servers, wherein they parsed malformed e-mail addresses and delivered it to the right mail server, and on the receiving end, the mail was delivered to the right mailbox.

	While not allowing us complete control over the e-mails sent, \texttt{To header injection} makes it possible to append any number of e-mail addresses, thereby enabling us to leak information, and/or perform DoS (Denial of Service) attacks.

@@

\input{Results/data_analysis}
We explain the combination of these header injections (4-7) as follows:
\begin{itemize}
	\item E-Mail Header Injections with \texttt{bcc} and \texttt{x-check} headers\\
	These represent the perfect attack scenario where we are able to inject multiple headers into the e-mails. We can see that over 70\% of the received \texttt{bcc} header injected e-mails are also susceptible to other header injections.

### 2016-05-19 Results/data_analysis.tex
final data update

\begin{table*}[!htbp]
	\centering
	\begin{tabular}{|l|c|}
		\hline
		\multicolumn{1}{|c|}{\textbf{Type of Injection}} &
		\multicolumn{1}{p{3cm}|}{\centering \textbf{No. of e-mails received}}\\
		\hline
		E-Mail Header Injections with \texttt{bcc} header & 304\\
		\hline
		E-Mail Header Injections with \texttt{x-check} header & 252\\
		\hline
		\texttt{To header} injections alone & 157\\
		\hline
		E-Mail Header Injections with \texttt{bcc} and \texttt{x-check} headers & 216\\
		\hline
		Both \texttt{To header} injections and x-check headers &
		12\\
		\hline
		\texttt{x-check} headers found in \texttt{nuser} e-mails & 67\\
		\hline
		Unique \texttt{x-check} headers found in \texttt{nuser} e-mails & 35\\
		\hline
		Total successful injections (1 + 3 + 7) & 496\\

>>>>

\begin{table*}[!htbp]
	\centering
	\begin{tabular}{|l|c|}
		\hline
		\multicolumn{1}{|c|}{\textbf{Type of Injection}} &
		\multicolumn{1}{p{3cm}|}{\centering \textbf{No. of e-mails received}}\\
		\hline
		E-Mail Header Injections with \texttt{bcc} header & 329\\
		\hline
		E-Mail Header Injections with \texttt{x-check} header & 396\\
		\hline
		\texttt{To header} injections alone & 163\\
		\hline
		E-Mail Header Injections with \texttt{bcc} and \texttt{x-check} headers & 216\\
		\hline
		Both \texttt{To header} injections and x-check headers &
		13\\
		\hline
		\texttt{x-check} headers found in \texttt{nuser} e-mails & 219\\
		\hline
		Unique \texttt{x-check} headers found in \texttt{nuser} e-mails & 181\\
		\hline
		Total successful injections (1 + 3 + 7) & \success\ \\
